Merge_PICO_Growth_PUR

### 2024-01-15 Code/Merge_GrowthPURData.Rmd
Changed folder name to Figures in PlotsPath

DataInPUR <- file.path("..", "Data", "ProcessedData", "ProcessedOlisJazData", fsep = .Platform$file.sep)
DataInGrowth <- file.path("..", "Data", "CleanData", "CleanedMCData", fsep = .Platform$file.sep)
DataOut <- file.path("..", "Data", "CleanData")
PlotsPath <- file.path("..", "Output", "Plots")

>>>>

DataInPUR <- file.path("..", "Data", "ProcessedData", "ProcessedOlisJazData", fsep = .Platform$file.sep)
DataInGrowth <- file.path("..", "Data", "CleanData", "CleanedMCData", fsep = .Platform$file.sep)
DataOut <- file.path("..", "Data", "CleanData")
PlotsPath <- file.path("..", "Output", "Figures")
